---
title: "GEOG5967 <br> <span style='font-size:.8em; font-weight: 500'>CAMS Dissertation</span> <br> <span style='font-size:.8em; font-weight: 500'>in Geography</span>"
subtitle: "<br><span style='color:#525252; font-size:1.0em;'>-- Spring/Summer 2024</span>"
format: 
   revealjs:
     transition: fade
     theme: theme/slides-theme.scss
     css: theme/style.css
     footer: '[Roger Beecham](https://roger-beecham.com)'
     mainfont: Avenir Book
---

## CAMS Dissertations


* **Important**  <br> Worth 30 credits

* **Interesting** <br> Chance to study something that matters to you

* **Independent** <br> Opportunity to work on substantive piece of work on your own

* **Initiative**  <br> Led by you

::: footer
:::

::: {.notes}

Go to Minerva.
Handbook : module information -- scan through -- 
            12k words etc.
            overview of dates 
            supervisor guidance 
            data guidance 
            subission specifics 
Learning Resources
             will post examples -- not necessarily good but indicatve
             
:::

---

## CAMS Geography Dissertations

* Module leader: Roger Beecham | Module team: Various

* In this session:
  + Choosing a dissertation topic
  + Finding data for a dissertation
  + Finding literature for a dissertation
  + Planning a dissertation

* E-mail `r.j.beecham@leeds.ac.uk` with your broad dissertation theme by **Friday 10th May** (20-30 words max)


::: footer
:::

::: {.notes}

:::

---

## CAMS Geography Dissertations

* Module leader: Roger Beecham | Module team: Various

* In this session:
  + Choosing a dissertation topic
  + Finding data for a dissertation
  + Finding literature for a dissertation
  + Planning a dissertation


:::{style="color: #a50f15;"}
* E-mail `r.j.beecham@leeds.ac.uk` with your broad dissertation theme by **Friday 10th May** (20-30 words max)
:::

::: footer
:::

::: {.notes}

:::

---

## CAMS Geography Dissertations

:::{.fragment .fade-in style="font-size: 90%;"}

> Involves some form of **spatial analysis** linked to any of the topics covered in the lectures and practical classes.

:::

:::{.fragment .fade-in style="font-size: 90%;"}

> Is **analytic** in nature, using any of the methods, tools and techniques covered in your Geography modules

:::

:::{.fragment .fade-in style="font-size: 90%;"}
> Uses **secondary data** from any of the broad type of sources that we have introduced.

:::

:::{.fragment .fade-in style="font-size: 90%;"}

> Represents a substantial piece of **academic research**, but can be carried out with input from a company or other external organisation.
:::

::: footer
:::

::: {.notes}

:::

---

# Choosing a topic

## Choosing a topic

:::{.columns}

::: {.column width="50%" style="font-size: 90%;"}

**Techniques** <br>

* Spatial pattern analysis
* Time series analysis
* Network analysis
* Machine Learning
  + regression, decision trees, clustering
* Empirical modelling
  + ABMs/microsimulation
* Data visualisation

:::

::: {.column width="50%" style="font-size: 90%;"}
**Themes** <br>

* Demographics
* Housing markets
* Consumer analytics/profiling
* Network planning
* Targeted marketing / Response modelling
* Inequalities and accessibility

:::

:::

::: footer
:::

::: {.notes}
Also technology : R, Python, others

Important : specfic and well-specified 

:::


---

## How to come up with an idea


:::{.fragment .fade-in style="font-size: 80%;"}

*  Identify **[aspects of the course]()** that have **interested you** and some of the readings that you have undertaken.  Are there aspects that you’d be able and **want to develop further**?

:::

:::{.fragment .fade-in style="font-size: 80%;"}

* Note some of the **[methods and technologies](https://www.tidymodels.org/)** used -- could you apply these to a different study area or a slightly different problem?

:::

:::{.fragment .fade-in style="font-size: 80%;"}
* Is there an **[interesting dataset](https://insideairbnb.com/)** that you’d like to explore further?

:::

:::{.fragment .fade-in style="font-size: 80%;"}

* Is there a **[particular issue](https://www.theguardian.com/society/2019/jan/28/improving-uk-cycling-rates-could-save-nhs-319m-says-report)** related to your home country or your previous study/employment that you could focus on.
:::

:::{.fragment .fade-in style="font-size: 80%;"}

* Have you read a research paper that [**especially interested you**](https://www.tandfonline.com/doi/full/10.1080/09593969.2021.2017321) -- could you carry out a similar study with some related data for Leeds/UK/home country?

:::

::: footer
:::

::: {.notes}

So understand requirements, thought about broad themes/topics that interest -- how to proceed?

Pick interesting paper/study/analysis read?

:::

---

## Example


::: footer
:::

::: {.notes}

Connected bikeability

Overarching message : don't over-complicate.
Best dissertations : build upon work already done.

:::

---

## Task 

<br>

Propose a broad dissertation topic, then write down:

* Is it linked to the objectives of my programme of study?

* Do I have sufficient interest in this topic to study it for the next 6 months?

* Do I have the necessary skills?

* Is sufficient data available and have I got access to it?

* Is there some relevant academic literature?

```{r}
#| label: ex-2-timer
countdown::countdown(
  minutes = 15,
  color_border = "#b20e10",
  color_text = "#b20e10",
  color_running_text = "white",
  color_running_background = "#b20e10",
  color_finished_text = "#b20e10",
  color_finished_background = "white",
  top = 0,
  margin = "0.5em",
  font_size = "2em"
)
```

::: footer
:::

::: {.notes}

Connected bikeability

Overarching message : don't over-complicate.
Best dissertations : build upon work already done.

:::

---

# Finding data

## Why is **data** so important to planning?




:::{.fragment .fade-in style="font-size: 80%;"}

*  Geography dissertations are **analytic** in nature, characterised by the application of spatial and statistical analysis techniques to analyse large-scale datasets.

:::

:::{.fragment .fade-in style="font-size: 80%;"}

* Geography dissertations are **secondary data analysis** projects, repurposing datasets that already exist.

:::

:::{.fragment .fade-in style="font-size: 80%;"}
* **CAMS** Geography dissertations are applied **data science** studies repurposing administrative, but also sometimes new, observational datasets.
:::




::: footer
:::

::: {.notes}

:::
---

## How to select **data**

1. Look back at the datasets you have used in **taught sessions**

2. Investigate some of the datasets suggested in the **dissertation module handbook** and during this session

3. Think back to some of the datasets you have seen via your **personal, social or academic networks**

::: footer
:::

::: {.notes}
Some dissertations present a coherent and interesting analysis using only a *single* dataset. Others combine several datasets.

:::

---

## Different categories of open dataset


:::{.fragment .fade-in }

1. Small area census and government data

:::

:::{.fragment .fade-in }

2. Open data portals

:::

:::{.fragment .fade-in }

3. Domain and dataset-specialised APIs
:::



::: footer
:::

::: {.notes}

:::
---

## Small area census and gov data

<br>

* UK Census and survey data from [`nomisweb`](https://www.nomisweb.co.uk/), [`UK Data Service`](https://ukdataservice.ac.uk/)

* US Census and survey data from [`US Census Bureau`](https://www.census.gov/), [`tidycensus`](https://walker-data.com/tidycensus/)


::: footer
:::

::: {.notes}

Demonstrate access via UK data service:

Geog precision, variable selection
:::

---

## Open data portals

* UK: [`Data Mill North`](https://datamillnorth.org/dataset), [`OpenManchester`](http://open.manchester.gov.uk/), [`data.gov.uk`](https://data.gov.uk/)

* Non-UK: [`data.melbourne`](https://data.melbourne.vic.gov.au/), [`opendata.cityofnewyork`](https://opendata.cityofnewyork.us/data/), [`data.gov.sg`](https://data.gov.sg/)


::: footer
:::

::: {.notes}

Demonstrate access via UK data service:

Geog precision, variable selection
:::

---

## Domain specific APIs

* Transport: [`stats19`](https://docs.ropensci.org/stats19/), [`TfL Open Data`](https://tfl.gov.uk/info-for/open-data-users/), [`bikedata`](https://docs.ropensci.org/bikedata/), [`moverment.uber`](https://movement.uber.com/?lang=en-GB), [`OpenFlights`](https://openflights.org/data.html)

* Crime: [`data.police.uk`](https://data.police.uk/), [`ukpolice`](https://docs.evanodell.com/ukpolice/)

* Health: [`covid-19 cases, deaths, vaccines`](https://coronavirus.data.gov.uk/details/download), [`covdata`](https://kjhealy.github.io/covdata/), [`covmobility`](https://kjhealy.github.io/covmobility/)

* User-generated: [`yelp.com`](https://www.yelp.com/dataset), [`twitter API`](https://developer.twitter.com/en/docs/twitter-api)

* Miscellany: [`awesome-public-datasets`](https://github.com/awesomedata/awesome-public-datasets)

::: footer
:::

::: {.notes}


:::

---

## Demo

* [`UK Data Service`](https://ukdataservice.ac.uk/)

*  [`stats19`](https://docs.ropensci.org/stats19/)

::: footer
:::

::: {.notes}


:::

---

## Task : class discussion

<br>

You have an (approximate) theme / themes for your dissertation, let's discuss ideas for potential datasets.

Instructions:

1. Record the approximate thematic area of your dissertation.
2. Identify any datasets that you have already considered -- or "don't know" if you have no idea of datasets.

```{r}
#| label: ex-3-timer
countdown::countdown(
  minutes = 15,
  color_border = "#b20e10",
  color_text = "#b20e10",
  color_running_text = "white",
  color_running_background = "#b20e10",
  color_finished_text = "#b20e10",
  color_finished_background = "white",
  top = 0,
  margin = "0.5em",
  font_size = "2em"
)
```

::: footer
:::

::: {.notes}

Connected bikeability

Overarching message : don't over-complicate.
Best dissertations : build upon work already done.

:::

---

# Finding literature

## Finding literature

* [University Library - Literature Search](https://library.leeds.ac.uk/info/1404/literature_searching/14/literature_searching_explained)

* [University Library - Using Newspapers](https://library.leeds.ac.uk/info/1105/newspapers)

* [Google Scholar](https://scholar.google.co.uk/)

* [Science Direct](https://www.sciencedirect.com/)

* [Web of Science](https://clarivate.com/products/scientific-and-academic-research/research-discovery-and-workflow-solutions/webofscience-platform/)

::: footer
:::

::: {.notes}

Connected bikeability

:::

---

# Planning your dissertation


## Process

:::{style="font-size: 80%;"}


* You are allocated a **supervisor** who will be able to provide advice and suggestions. You will usually meet with them 4 – 6 times during your research.

* You will e-mail a **1-page research plan** on **Friday 7th June** to your supervisor.

* You will receive oral feedback on your research plan in **June**.

* Most of your research will be carried out over the summer (June – August) and must be completed independently.

* Submit your final dissertation on **Thursday 29th August before 2pm**.

* The **maximum word limit** for your dissertation is 12,000 words, many may be considerably shorter than this.

:::

::: footer
:::

::: {.notes}

:::

---

## 1-page dissertation plan

:::{style="font-size: 70%;"}

1. **Title** | Likely this will change

2. **Research questions / aims** | What you hope to achieve

3. **Research tasks** | The activities/steps you will take to achieve your aims

4. **Why this topic is interesting, relevant, topical**
  + Why this topic interests you
  + Academic interest in the topic area -- with some appropriate academic literature
  + Only if appropriate, the wider commercial or public interest in the topic

5. **Methods** | Include high-level details
  + List and describe datasets: how collected, size, geographic scale, temporal coverage
  + Tools/techniques/methods/software you will use to analyse your data -- how and why
  + Address how these will help engage with research aims

:::
---

## Supervisors

<br>

:::{style="font-size: 90%;"}

> Your **dissertation supervisor is your primary contact** and you should deal directly with them for support and advice.
>
> But: You must take initiative to develop and manage your dissertation.
>
> Note: Supervisors are there for guidance and advice but you lead your individual projects.

:::

---

## Help and support

:::{style="font-size: 80%;"}

* Your **dissertation supervisor is your primary contact** and you should deal directly with them for support and advice.

* Roger (`r.j.beecham@leeds.ac.uk`) manages the dissertation module. Contact him with administrative queries or issues that you have not been able to resolve with your supervisor.

* Claire Gorner (`c.gorner@leeds.ac.uk`) in the Geography Student Support Office is your contact for any personal issues affecting your progress or for deadline extensions.

* **New** : Dedicated GIS/Coding support from PGR + academic practice support from Na Yan (n.yan@leeds.ac.uk). Details to follow.

:::

---

## Next steps

:::{style="font-size: 80%;"}

* E-mail to me (Roger Beecham) your 20-30 word outline by **Friday 10th May**.

* Contact your supervisor for your **single** meeting with them before you hand in your 1-page dissertation plan.

* Prepare your dissertation plan, submit it **via e-mail by Friday 7th Jun**.

* You should receive feedback on your dissertation plan via a meeting and have three meetings with your supervisor to:
  + Discuss data preparation, lit review and methods
  + Troubleshoot analysis and discuss outputs
  + Discuss findings and write-up

:::



