---
title: "<span style='font-size:.8em;'><br> Addressing Environment and Sustainability Challenges though Data-Driven Science </span>"
subtitle: "<span style='font-size:1.3em;'><br>1200--1400 <br>Clarendon GR.01 </span>
"
format: 
   revealjs:
     transition: fade
     theme: [default, theme/slides-theme.scss]
     css: theme/style.css
     footer: 'Faculty of Environment | Leeds Institute for Data Analytics'
     mainfont: Jost
     logo: "https://comms.leeds.ac.uk/wp-content/uploads/sites/51/2021/04/Visual-identity-section-images--e1618925864440.png"
---

::: {style="font-size: 110%; font-weight: 550;"}
Addressing Environment and Sustainability Challenges though Data-Driven Science
:::

::: {style="font-size: 85%;"}
* 1200--1220 : Lunch
* 1220--1230 : Welcome <br> <span style='font-size:0.8em;'>-- *Alan Haywood and Susan Grant Muller* </span>
* 1230--1345 : Lightning talks <br>
<span style='font-size:0.8em;'>-- *Yuchen Li* </span> <br> 
<span style='font-size:0.8em;'>-- *Weiming Huang* </span><br> 
<span style='font-size:0.8em;'>-- *Trystan Surawy Stepney* </span><br> 
<span style='font-size:0.8em;'>-- *Yuanxuan Yang* </span><br> 
<span style='font-size:0.8em;'>-- *Jennifer Sexton* </span><br>
<span style='font-size:0.8em;'>-- *Chetan Devan* </span><br>
<span style='font-size:0.8em;'>-- *Ramesh Nadarajah* </span>
* 1345--1400 : Networking

:::



---

::: {style="font-size: 110%; font-weight: 550;"}
Addressing Environment and Sustainability Challenges though Data-Driven Science
:::

::: {style="font-size: 85%;"}
* 1200--1220 : **Lunch**
* 1220--1230 : Welcome <br> <span style='font-size:0.8em;'>-- *Alan Haywood and Susan Grant Muller* </span>
* 1230--1340 : Lightning talks <br>
<span style='font-size:0.8em;'>-- *Yuchen Li* </span> <br> 
<span style='font-size:0.8em;'>-- *Weiming Huang* </span><br> 
<span style='font-size:0.8em;'>-- *Trystan Surawy Stepney* </span><br> 
<span style='font-size:0.8em;'>-- *Yuanxuan Yang* </span><br> 
<span style='font-size:0.8em;'>-- *Jennifer Sexton* </span><br>
<span style='font-size:0.8em;'>-- *Chetan Devan* </span><br>
<span style='font-size:0.8em;'>-- *Ramesh Nadarajah* </span>
* 1340--1400 : Networking

:::


```{r}
countdown::countdown(
  minutes = 20,
  color_border = "#b20e10",
  color_text = "#b20e10",
  color_running_text = "white",
  color_running_background = "#b20e10",
  color_finished_text = "#b20e10",
  color_finished_background = "white",
  bottom = 0,
  margin = "0.5em",
  font_size = "2em"
)
```



---

::: {style="font-size: 110%; font-weight: 550;"}
Addressing Environment and Sustainability Challenges though Data-Driven Science
:::

::: {style="font-size: 85%;"}
* 1200--1220 : Lunch
* 1220--1230 : **Welcome** <br> <span style='font-size:0.8em;'>-- *Alan Haywood and Susan Grant Muller* </span>
* 1230--1340 : Lightning talks <br>
<span style='font-size:0.8em;'>-- *Yuchen Li* </span> <br> 
<span style='font-size:0.8em;'>-- *Weiming Huang* </span><br> 
<span style='font-size:0.8em;'>-- *Trystan Surawy Stepney* </span><br> 
<span style='font-size:0.8em;'>-- *Yuanxuan Yang* </span><br> 
<span style='font-size:0.8em;'>-- *Jennifer Sexton* </span><br>
<span style='font-size:0.8em;'>-- *Chetan Devan* </span><br>
<span style='font-size:0.8em;'>-- *Ramesh Nadarajah* </span>
* 1340--1400 : Networking

:::


```{r}
countdown::countdown(
  minutes = 10,
  color_border = "#b20e10",
  color_text = "#b20e10",
  color_running_text = "white",
  color_running_background = "#b20e10",
  color_finished_text = "#b20e10",
  color_finished_background = "white",
  bottom = 0,
  margin = "0.5em",
  font_size = "2em"
)
```

---

::: {style="font-size: 110%; font-weight: 550;"}
Addressing Environment and Sustainability Challenges though Data-Driven Science
:::

::: {style="font-size: 85%;"}
* 1200--1220 : Lunch
* 1220--1230 : Welcome <br> <span style='font-size:0.8em;'>-- *Alan Haywood and Susan Grant Muller* </span>
* 1230--1340 : **Lightning talks** <br>
<span style='font-size:0.8em;'>-- *Yuchen Li* </span> <br> 
<span style='font-size:0.8em;'>-- *Weiming Huang* </span><br> 
<span style='font-size:0.8em;'>-- *Trystan Surawy Stepney* </span><br> 
<span style='font-size:0.8em;'>-- *Yuanxuan Yang* </span><br> 
<span style='font-size:0.8em;'>-- *Jennifer Sexton* </span><br>
<span style='font-size:0.8em;'>-- *Chetan Devan* </span><br>
<span style='font-size:0.8em;'>-- *Ramesh Nadarajah* </span>
* 1340--1400 : Networking

:::


```{r}
countdown::countdown(
  minutes = 70,
  color_border = "#b20e10",
  color_text = "#b20e10",
  color_running_text = "white",
  color_running_background = "#b20e10",
  color_finished_text = "#b20e10",
  color_finished_background = "white",
  bottom = 0,
  margin = "0.5em",
  font_size = "2em"
)
```

---

::: {style="font-size: 110%; font-weight: 550;"}
Addressing Environment and Sustainability Challenges though Data-Driven Science
:::

::: {style="font-size: 85%;"}
* 1200--1220 : Lunch
* 1220--1230 : Welcome <br> <span style='font-size:0.8em;'>-- *Alan Haywood and Susan Grant Muller* </span>
* 1230--1340 : Lightning talks <br>
<span style='font-size:0.8em;'>-- *Yuchen Li* </span> <br> 
<span style='font-size:0.8em;'>-- *Weiming Huang* </span><br> 
<span style='font-size:0.8em;'>-- *Trystan Surawy Stepney* </span><br> 
<span style='font-size:0.8em;'>-- *Yuanxuan Yang* </span><br> 
<span style='font-size:0.8em;'>-- *Jennifer Sexton* </span><br>
<span style='font-size:0.8em;'>-- *Chetan Devan* </span><br>
<span style='font-size:0.8em;'>-- *Ramesh Nadarajah* </span>
* 1340--1400 : **Networking**

:::


```{r}
countdown::countdown(
  minutes = 20,
  color_border = "#b20e10",
  color_text = "#b20e10",
  color_running_text = "white",
  color_running_background = "#b20e10",
  color_finished_text = "#b20e10",
  color_finished_background = "white",
  bottom = 0,
  margin = "0.5em",
  font_size = "2em"
)
```