---
title: "Chapter 09 Template"
author: "Roger Beecham"
format: html
editor_options: 
  chunk_output_type: console
---

## Introduction

Reopen your project and save this `.qmd` file in the top-level folder. When working through the materials from this chapter run each code chunk separately by clicking the small green arrow beside each code chunk. By default I have set `eval: false` on most code chunks, so when you knit the code chunk will not execute.


## Setup

The code block below points to the packages you need. 

```{r}
#| echo: true
#| eval: false
library(tidyverse) 
library(sf)
library(here)
```

Bring in the staged Covid-19 case data by US county, as well as the `.geojson` files for US states and counties. Note that the Covid-19 case data were originally collected via the [`covdata`](https://kjhealy.github.io/covdata/) R package.

```{r}
#| echo: true
#| eval: false
url <- "https://vis4sds.github.io/data/ch8/county_data_covid.csv"
download.file(url, here("data", "county_data_covid.csv"))
county_data <- read_csv(here("data", "county_data_covid.csv")) |> 
  mutate(binned_growth_rate = factor(binned_growth_rate))

url <- "https://vis4sds.github.io/data/ch8/county_boundaries.geojson"
download.file(url, here("data", "county_boundaries.geojson"))
county_boundaries <- st_read(here("data", "county_boundaries.geojson"))  

url <- "https://vis4sds.github.io/data/ch8/state_boundaries.geojson" 
download.file(url, here("data", "state_boundaries.geojson"))              
state_boundaries <- st_read(here("data", "state_boundaries.geojson"))  
```


```{r}
p <- county_data |> 
  ggplot()+
  geom_sf(
    data=state_boundaries, 
    fill="#eeeeee", colour="#ffffff", linewidth=0.4
  )+ 
  coord_sf(crs = 5070, datum=NA, clip="off") +
  geom_point(
    data=.%>% filter(date=="2020-05-03"), 
    aes(x=x, y=y, size=case_rate, alpha=binned_growth_rate, colour=binned_growth_rate)
  ) +
  # Plot case data.
  geom_path(
    aes(x=x+((day_num-1)*6000), y=y+((growth_rate-1)*50000), 
        group=fips, linewidth=case_rate, alpha=binned_growth_rate, colour=binned_growth_rate
    ),
    lineend="round"
  ) +
  scale_colour_manual(values=c("#fa9fb5", "#dd3497", "#7a0177", "#49006a")) +
  scale_size(range=c(.1,1.5))+
  scale_linewidth(range=c(.3,3))+
  scale_alpha_ordinal(range=c(.2,1)) +
  guides(colour="none", size="none", alpha="none", linewidth = "none") +
  theme_void()




  # 5070 flattens out the US
  coord_sf(crs = 5070, datum=NA, clip="off") +
  geom_point(
    data=.%>% filter(date=="2020-05-03"), 
    aes(x=x, y=y, size=case_rate, alpha=binned_growth_rate, colour = binned_growth_rate)
  ) +
  # Plot case data.
  geom_path(
    aes(x=x+((day_num-1)*6000), y=y+((growth_rate-1)*50000), 
        # fips is a country code, ensures that there will be separate lines ->
        # group lines by country, so it does not get plotted as one line
        group=fips, linewidth=case_rate, alpha=binned_growth_rate
    ),
    lineend="round"
  ) +
  
  scale_colour_manual(values=c("#fa9fb5", "#dd3497", "#7a0177", "#49006a")) +
  scale_size(range=c(.1,1.5))+
  scale_linewidth(range=c(.3,3))+
  scale_alpha_ordinal(range=c(.2,1)) +
  # removing parts of legend
  guides(colour="none", size="none", alpha="none", linewidth="none") +
  theme_void()
```

```{r}
# Counties to annotate.
annotate <- county_data |>  
  filter(
    date=="2020-05-03",
    county==c("Huntingdon") & state=="Pennsylvania" |
    county==c("Lenawee") & state=="Michigan" |
    county==c("Crawford") & state=="Iowa" |
    county==c("Wapello") & state=="Iowa" |
    county==c("Lake") & state=="Tennessee" |
    county=="Texas" & state == c("Oklahoma") |
    county==c("Duplin") & state=="North Carolina" |
    county==c("Santa Cruz") & state=="Arizona"|
    county==c("Titus") & state=="Texas"|
    county==c("Yakima") & state=="Washington"
    ) |> 
  mutate(
    state_abbr=case_when(
      state=="Pennsylvania" ~ "Penn.",
      state=="Iowa" ~ "Iowa",
      state=="Tennessee" ~ "Tenn.",
      state=="Oklahoma" ~ "Okla.",
      state=="Texas" ~ "Texas",
      state=="North Carolina" ~ "N.C.",
      state=="Washington" ~ "Wash.",
      state=="Michigan" ~ "Mich.",
      state=="Arizona" ~ "Arizona",
      TRUE ~ ""),
    end_rate_round = round(end_rate,0)
  )
```


```{r}

  
p +   
  # adds state abbreviation to the map (center of state)
  geom_text(data = state_boundaries, aes(x = x, y = y, label = STUSPS), alpha = .8) +
  # adds the county, state label to selected states (highlighting parts of the map)
  # specified in annotate object
  # offsetting y ?? +
  geom_text(
    data=annotate, 
    aes(x=x,y=y-20000,label=paste0(county,", ",state_abbr)), 
    size=3, fontface="bold"
    )+
  geom_text(
    data=annotate, 
    aes(x=x,y=y-65000,label=paste0(end_rate_round,"X more cases")), 
    size=2.5
    )


```

```{r}
# Bounding box for mainland US.
bbox <- st_bbox(state_boundaries)
width <- bbox$xmax-bbox$xmin
height <- bbox$ymax-bbox$ymin
```



```{r}
growth_text <- "Line height and colour show change in reported cases 
relative to May 3"
case_text <- "Line thickness shows current number relative to 
county population"
title_text <- "Change in reported cases since May 3"


# Legend : case
legend_case <- county_data |>
  # finding one county shape for growth that I like
  filter(
    county == "Kings" & state=="California" ) |>
  mutate(
    x=bbox$xmax-.88*width,y=bbox$ymax+.05*height,
    binned_growth_rate=factor(binned_growth_rate)
  ) %>%
  select(x, y, day_num, growth_rate, binned_growth_rate, fips) |>
  mutate(
    low=.001, mid=.009, high=.015,
  ) |>
  # same data repeated for low, mid, high, with changed growth_rate var
  pivot_longer(cols=c(low, mid, high), names_to="offset", values_to="offset_rate") |>
  # moving in geographic space, so there is space between lines for (less, more cases)
  mutate(
    offset_day= case_when(
      offset == "low" ~ 0,
      offset == "mid" ~ .04,
      offset == "high" ~ .08
    )
  )

```



```{r}
p +
  geom_text(data = state_boundaries, aes(x = x, y = y, label = STUSPS), alpha = .8) +
  geom_text(
    data = annotate,
    aes(x = x, y = y - 20000, label = paste0(county, ", ", state_abbr)),
    size = 3, fontface = "bold"
  ) +
  ## Adding a second line to highlight, adding 
  geom_text(
    data = annotate,
    aes(x = x, y = y - 65000, label = paste0(end_rate_round, "X more cases")),
    size = 2.5
  ) +
  theme_void() +
  geom_path(
    data = legend_growth,
    aes(
      x = x + ((day_num - 1) * 6000), y = y + ((growth_rate - 1) * 50000),
      group = fips, linewidth = case_rate,
      colour = binned_growth_rate # throws error continuous value supplied to discrete
    ),
    lineend = "round"
  ) +
  # Text label for growth legend lines.
  geom_text(
    # For positioning manually edit growth_rate of Bledsoe.
    data = legend_growth %>% filter(day_num == max(county_data$day_num)) %>%
      mutate(growth_rate = if_else(county == "Bledsoe", -1, growth_rate)),
    aes(
      x = x + (day_num * 6000) + 10000, y = y + ((growth_rate - 1) * 50000),
      label = str_wrap(label, 15)
    ),
    size = 2.5
  ) +
  annotate("text",
    x = bbox$xmax - .25 * width, y = bbox$ymax + .08 * height,
    label = str_wrap(growth_text, 35), size = 3.5, hjust = 1
  ) +

  # Plot case legend lines.
  geom_path(
    data = legend_case,
    aes(
      x = x + ((day_num - 1) * 6000) + offset_day * width, y = y + ((growth_rate - 1) * 50000),
      group = paste0(fips, offset), linewidth = offset_rate, 
      color = binned_growth_rate, 
      lineend = "round"
    )
  ) +
  # Text label for case legend lines.
  annotate("text",
    x = bbox$xmax - .88 * width, y = bbox$ymax + .04 * height, label = "Less", size = 2.5
  ) +
  annotate("text",
    x = bbox$xmax - .8 * width, y = bbox$ymax + .04 * height, label = "More", size = 2.5
  ) +
  annotate("text",
    x = bbox$xmax - .75 * width, y = bbox$ymax + .08 * height, label = str_wrap(case_text, 35),
    size = 3.5, hjust = 0
  ) +

  # Title.
  annotate("text",
    x = bbox$xmax - .5 * width, y = bbox$ymax + .15 * height, label = title_text, size = 5
  ) 
```

